Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-01-28 Report/dual_approach.tex
updated final with kkt conditions
changes with satya
halfcooked

&& \qquad {} \qquad {} + \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + N_0\|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-dual-1d} \\

@@

	\underset{\substack{\gamma_{l,k,n}, \mvec{W}{k,n},\mvec{M}{k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} && \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right ) \vspace{-0.25cm} \nonumber \\
	&& + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \vspace{-0.25cm} \\

@@

	+ \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L && |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + N_0\|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \eqspace \label{eqn-dual-1d} \\

@@

Now, the local problem \eqref{eqn-dual-3} at each \ac{BS} \me{b} is solved either by the \ac{SCA} approach discussed in Section \ref{sec-3.2.1} or by using the \ac{MSE} reformulation approach outlined in Section \ref{sec-3.3}. Once the local problems are solved at each \ac{BS}, the new update for the global interference vector \me{\mbfa{\zeta}^{(i)}} and the dual variables \me{\mbfa{\nu}^{\set{b}(i)}} are performed at each \ac{BS} independently by exchanging the corresponding local copies of the interference vector \me{\mbfa{\zeta}^{\set{b}(i)}, \forall b \in \mc{B}}. Since the entries in \me{\mbfa{\zeta}^{(i)}} relate exactly to two \acp{BS} only, each entry in \me{\mbfa{\zeta}^{(i)}} can be updated by exchanging the local copies from the corresponding two \acp{BS}. For instance, the entry \me{\zeta^{(i)}_{l,\mc{U}_{b_k}(1),n,b}} depends on the local interference value \me{\zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b}} assumed by the \ac{BS} \me{b_k} and the actual interference caused by \ac{BS} \me{b} as in \me{\zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b}} as
\begin{equation}
\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(i)} = \frac{1}{2} \, \left ( \, \zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b} + \zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b} \, \right ).
\label{zeta_update}
\end{equation}
The dual variable vector \me{\mbfa{\nu}^{\set{b_k}}}, which includes the stacked dual variables of the interference equality constraint at \ac{BS} \me{b_k}, are updated using the subgradient as
\begin{equation}\label{dual-sg-update}
\nu^{\set{b_k}(i)}_{l,k,n,b} = \nu^{\set{b_k}(i-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(i)}_{l,k,n,b} - \zeta^{(i)}_{l,k,n,b} \right ).
\end{equation}
The distributed precoder design using \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
{\allowdisplaybreaks 
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
	\KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{eqn-4.3}}
	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} \;
	initialize the global interference vectors \me{\mbfa{\zeta}^{(0)} = \mbfa{0}^{\mathrm{T}}} \;
	initialize the interference threshold \me{\mbfa{\nu}^{\set{b}(0)} \forall b \in \mc{B} = 0} \;
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{convergence or \me{i \geq I_{\max}}}{
			initialize \me{j=0} \;
			\Repeat{convergence or \me{j \geq J_{\max}}}{
				solve for \me{\mvec{M}{k,n}} and the local interference \me{\mbfa{\zeta}^{\set{b}}} using \eqref{eqn-dual-3} \;
				exchange \me{\mbfa{\zeta}^{\set{b}(j)}} among \acp{BS} in \me{\mc{B}} \;
				update dual variables in \me{\mbfa{\nu}^{\set{b}(j+1)}} using \eqref{dual-sg-update}\;
				update the consensus vector \me{\mbfa{\zeta}^{(j+1)}} using \eqref{zeta_update}\;
				\me{j = j + 1}\;
			}
			downlink precoded pilot transmission with \me{\mvec{M}{k,n}}\;
			update \me{\mvec{W}{k,n}} and notify to all \acp{BS} in \me{\mc{B}} using uplink precoded pilots as in \cite{komulainen2013effective}\;
			update \me{\tilde{\mbfa{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} approach \;
			$i = i + 1$ \;
		}
	}
	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
	\label{algo-3}
\end{algorithm}}

\subsubsection*{Convergence}
The convergence of the \ac{ADMM} method follows the same argument as the centralized algorithm if each distributed algorithm is allowed to converge to a stationary value for the fixed \ac{SCA} point. Since the subproblem solved at each \ac{BS} is convex, the \ac{ADMM} method converges to a stationary point \cite{boyd2011distributed} for the fixed \ac{SCA} value. The receive beamformers are updated along with the \ac{SCA} update of \me{\tilde{\mbf{u}}_{l,k,n}}. Combining the receiver update with the \ac{SCA} update improves the convergence speed due to the fact that the \ac{MMSE} receivers are optimal for the fixed transmit beamformers, providing monotonic increase in the objective function.

>>>>

&& \qquad {} \qquad {} + \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + \enoise \IEEEyessubnumber \label{eqn-dual-1d} \\

@@

	\underset{\substack{\gamma_{l,k,n}, \mvec{W}{k,n},\mvec{M}{k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} && \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right )  \nonumber \\
	&& + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a}  \\

@@

	+ \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L && |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + \enoise \IEEEyessubnumber \eqspace \label{eqn-dual-1d} \\

@@

Now, the local problem \eqref{eqn-dual-3} at each \ac{BS} \me{b} is solved either by the \ac{SCA} approach discussed in Section \ref{sec-3.2.1} or by using the \ac{MSE} reformulation approach outlined in Section \ref{sec-3.3}. Once the local problems are solved at each \ac{BS}, the new update for the global interference vector \me{\mbfa{\zeta}^{(i)}} and the dual variables \me{\mbfa{\nu}^{\set{b}(i)}} are performed at each \ac{BS} independently by exchanging the corresponding local copies of the interference vector \me{\mbfa{\zeta}^{\set{b}(i)}, \forall b \in \mc{B}}. Since the entries in \me{\mbfa{\zeta}^{(i)}} relate exactly to two \acp{BS} only, each entry in \me{\mbfa{\zeta}^{(i)}} can be updated by exchanging the local copies from the corresponding two \acp{BS}. For instance, the entry \me{\zeta^{(i)}_{l,\mc{U}_{b_k}(1),n,b}} depends on the local interference value \me{\zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b}} assumed by the \ac{BS} \me{b_k} and the actual interference caused by \ac{BS} \me{b} as in \me{\zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b}} as
\begin{equation}
\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(i)} = \frac{1}{2} \, \left ( \, \zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b} + \zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b} \, \right ).
\label{zeta_update}
\end{equation}
The dual variable vector \me{\mbfa{\nu}^{\set{b_k}}}, which includes the stacked dual variables of the interference equality constraint at \ac{BS} \me{b_k}, are updated using the subgradient as
\begin{equation}\label{dual-sg-update}
\nu^{\set{b_k}(i)}_{l,k,n,b} = \nu^{\set{b_k}(i-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(i)}_{l,k,n,b} - \zeta^{(i)}_{l,k,n,b} \right ).
\end{equation}
The distributed precoder design using \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
{\allowdisplaybreaks 
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
	\KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{eqn-4.3}}
	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} \;
	initialize the global interference vectors \me{\mbfa{\zeta}^{(0)} = \mbfa{0}^{\mathrm{T}}} \;
	initialize the interference threshold \me{\mbfa{\nu}^{\set{b}(0)} \forall b \in \mc{B} = 0} \;
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{convergence or \me{i \geq I_{\max}}}{
			initialize \me{j=0} \;
			\Repeat{convergence or \me{j \geq J_{\max}}}{
				solve for \me{\mvec{m}{l,k,n}} and the local interference \me{\mbfa{\zeta}^{\set{b}}} using \eqref{eqn-dual-3} \;
				exchange \me{\mbfa{\zeta}^{\set{b}(j)}} among \acp{BS} in \me{\mc{B}} \;
				update dual variables in \me{\mbfa{\nu}^{\set{b}(j+1)}} using \eqref{dual-sg-update}\;
				update the consensus vector \me{\mbfa{\zeta}^{(j+1)}} using \eqref{zeta_update}\;
				\me{j = j + 1}\;
			}
			downlink precoded pilot transmission with \me{\mvec{m}{k,n}}\;
			update \me{\mvec{l}{k,n}} and notify to all \acp{BS} in \me{\mc{B}} using uplink precoded pilots as in \cite{komulainen2013effective}\;
			update \me{{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} approach \;
			$i = i + 1$ \;
		}
	}
	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
	\label{algo-3}
\end{algorithm}}

\begin{comment}
\subsubsection*{Convergence}
The convergence of the \ac{ADMM} method follows the same argument as the centralized algorithm if each distributed algorithm is allowed to converge to a stationary value for the fixed \ac{SCA} point. Since the subproblem solved at each \ac{BS} is convex, the \ac{ADMM} method converges to a stationary point \cite{boyd2011distributed} for the fixed \ac{SCA} value. The receive beamformers are updated along with the \ac{SCA} update of \me{\tilde{\mbf{u}}_{l,k,n}}. Combining the receiver update with the \ac{SCA} update improves the convergence speed due to the fact that the \ac{MMSE} receivers are optimal for the fixed transmit beamformers, providing monotonic increase in the objective function.
\end{comment}

### 2015-01-28 Report/kkt_mse_approach.tex
halfcooked

With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
\iftoggle{single_column}{\allowdisplaybreaks
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \hspace{0.5cm} & \nonumber \\
\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  \enoise + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \eqspace \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}{
\begin{IEEEeqnarray}{Rl}\label{kkt-mse-1}
	\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} & \quad \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
	\text{subject to} & \nonumber \\
	\alpha_{l,k,n} : &  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  \enoise \nonumber \\
	& + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
	\sigma_{l,k,n} : &  \log_2(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2)\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.3} \\
	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}.

@@

The \ac{KKT} expressions in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the transmit and the receive beamformers \me{\mvec{M}{k,n},\mvec{W}{k,n}} with the single user beamforming and the \ac{MMSE} vectors. The dual variable \me{\alpha}'s are initialized with ones to have equal priorities to all the users in the system. Then the transmit and the receive beamformers are evaluated using the expressions in \eqref{kkt-mse-4}. The transmit precoder in \eqref{kkt-mse-4.3} depends on the \ac{BS} specific dual variable \me{\delta_b}, which can be found by bisection search satisfying the total power constraint \eqref{kkt-mse-1.4}. Note that the fixed \ac{SCA} operating point is given by \me{\tilde{\epsilon}_{l,k,n} = \epsilon_{l,k,n}^{(i-1)}}, which is considered in the expression \eqref{kkt-mse-4}.

@@

	update \me{\mvec{M}{k,n}^{(i)}} using \eqref{kkt-mse-4.3}, and perform downlink transmission \;
	find \me{\mvec{W}{k,n}^{(i)}} using \eqref{kkt-mse-4.6} at each user \;
	evaluate \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at each user with the updated \me{\mvec{W}{k,n}^{(i)}} \;
	using precoded uplink pilots, \me{\mvec{W}{k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} are notified to all \acp{BS} in \me{\mathcal{B}} \;

>>>>

With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
\iftoggle{single_column}{\allowdisplaybreaks
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n}, \\ \epsilon_{l,k,n}, \mvec{w}{l,k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \hspace{0.5cm} & \nonumber \\
\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  \enoise + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \eqspace \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}{
\begin{IEEEeqnarray}{Rl}\label{kkt-mse-1}
	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n}, \\ \epsilon_{l,k,n}, \mvec{w}{l,k,n}}}{\text{minimize}} & \quad \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
	\text{subject to} & \nonumber \\
	\alpha_{l,k,n} : &  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  \enoise \nonumber \\
	& + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
	\sigma_{l,k,n} : &  \log_2(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2)\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.3} \\
	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}.

@@

The \ac{KKT} expressions in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the transmit and the receive beamformers \me{\mvec{m}{l,k,n},\mvec{w}{l,k,n}} with the single user beamforming and the \ac{MMSE} vectors. The dual variable \me{\alpha}'s are initialized with ones to have equal priorities to all the users in the system. Then the transmit and the receive beamformers are evaluated using the expressions in \eqref{kkt-mse-4}. The transmit precoder in \eqref{kkt-mse-4.3} depends on the \ac{BS} specific dual variable \me{\delta_b}, which can be found by bisection search satisfying the total power constraint \eqref{kkt-mse-1.4}. Note that the fixed \ac{SCA} operating point is given by \me{\tilde{\epsilon}_{l,k,n} = \epsilon_{l,k,n}^{(i-1)}}, which is considered in the expression \eqref{kkt-mse-4}.

@@

	update \me{\mvec{m}{l,k,n}^{(i)}} using \eqref{kkt-mse-4.3}, and perform downlink transmission \;
	find \me{\mvec{w}{l,k,n}^{(i)}} using \eqref{kkt-mse-4.6} at each user \;
	evaluate \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at each user with the updated \me{\mvec{w}{l,k,n}^{(i)}} \;
	using precoded uplink pilots, \me{\mvec{m}{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} are notified to all \acp{BS} in \me{\mathcal{B}} \;

### 2015-01-28 Report/sub_channel_wsrm.tex
halfcooked

The complexity involved in the \ac{JSFRA} scheme scales significantly with the increase in the number of sub-channels considered in the formulation. In addition to the increased complexity, the rate of convergence to the optimal precoders also degrades due to its dependency on the problem size. In order to mitigate this, we can adopt the decomposition techniques discussed in \cite{palomar2006tutorial,boyd2011distributed} to distribute the precoder design across each sub-channels independently with some coupling parameters that are exchanged across the sub-channel wise subproblems.

As an alternative sub-optimal solution, we propose \acl{QM} \ac{SRA}, which aims at designing the precoders independently across each sub-channel in a sequential manner by taking the current backlogged packets into account. In this approach, the transmit power is fixed across each sub-channel \me{n} as \me{P_{\max,n}} at each \ac{BS}. The power split can either follow equal sharing or any predetermined pattern as in partial frequency reuse. For the fixed sub-channel power, the \ac{JSFRA} formulation presented in Section \ref{sec-3.2.1} or \ref{sec-3.3} is performed over each sub-channel in a sequential manner. The coupling variable across the sub-channel is the total number of backlogged packets associated with each user. 
Let \me{Q_{k,n}} is the total number of queued bits used in the optimization problem carried out for the sub-channel \me{n}. Now, for the first sub-channel, \me{n=1}, the queues are given by \me{Q_{k,n=1} = Q_k}, which corresponds to the actual number of backlogged packets present in the current instant \me{i}. Using the updated number of queued packets, the \ac{JSFRA} algorithm is performed over the sub-channel \me{n=1} to obtain the rates associated with each user. Now, for \me{n=2}, the number of queued packets for each user is updated as \me{Q_{k,n=2} = Q_k - \sum_{l=0}^L t_{l,k,n=1}}. With this updated number of queued packets, the \ac{JSFRA} algorithm is performed for \me{n=1} sub-channel to obtain the optimal precoders. In general, the number of queued packets to be used for each user in a given sub-channel \me{n} is given by
\begin{equation}
Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{r = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,r} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}.
\label{eqn-weight}
\end{equation}
In \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,r}} is the rate or guaranteed bits allocated over the sub-channel \me{r}. However, the proposed scheme is sensitive to the order in which the sub-channels are selected for the optimization problem.

>>>>

The complexity of the \ac{JSFRA} algorithm scales with the number of sub-channels considered. In addition, the iterations required for the convergence of the algorithm increases with the problem size. In order to overcome the complexity, we can perform the distributed approaches presented in \cite{palomar2006tutorial,boyd2011distributed} for sub-channel wise precoder design using primal or dual decomposition.

As an alternative sub-optimal solution, we present \acl{QM} \ac{SRA}, which design precoders independently across the sub-channels in a sequential manner using the unserviced number of packets after each sub-channel. The transmit power is fixed across each sub-channel \me{n} as \me{P_{\max,n}} for each \ac{BS}. The power either be equal sharing or based on predetermined pattern as in partial frequency reuse. For a fixed sub-channel power, the \ac{JSFRA} formulation presented in Section \ref{sec-3.2.1} or \ref{sec-3.3} is performed over each sub-channel in a sequential manner. The coupling variable across the sub-channel is the total number of backlogged packets associated with each user. 
Let \me{Q_{k,n}} is the total number of queued bits used in the optimization problem carried out for the sub-channel \me{n}. Now, for the first sub-channel, \me{n=1}, the queues are given by \me{Q_{k,n=1} = Q_k}, which corresponds to the actual number of backlogged packets present in the current instant \me{i}. Using the updated number of queued packets, the \ac{JSFRA} algorithm is performed over the sub-channel \me{n=1} to obtain the rates associated with each user. Now, for \me{n=2}, the number of queued packets for each user is updated as \me{Q_{k,n=2} = Q_k - \sum_{l=0}^L t_{l,k,n=1}}. With this updated number of queued packets, the \ac{JSFRA} algorithm is performed for \me{n=1} sub-channel to obtain the optimal precoders. In general, the number of queued packets to be used for each user in a given sub-channel \me{n} is given by
\begin{equation}
Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{r = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,r} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}.
\label{eqn-weight}
\end{equation}
In \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,r}} is the rate or guaranteed bits allocated over the sub-channel \me{r}. However, the proposed scheme is sensitive to the order in which the sub-channels are selected for the optimization problem.
